MS Keyrun Dataset Dimensions

### 2020-11-27 docs/DatasetDimensions.Rmd
hyperlink added to allocateLandingsEPU page

Ideal: Define using Georges Bank EPU, scale fisheries catch for each species from stat areas to GB EPU footprint using ratios in spatially explicit VTR subset of catch data. Work towards this ideal, comparing coverage of VTR data by species and different methods for scaling as part of data documentation. Consult with ADIOS team and assessment experts to see if results look reasonable.

>>>>

Ideal: Define using Georges Bank EPU, scale fisheries catch for each species from stat areas to GB EPU footprint using [ratios in spatially explicit VTR subset of catch data](allocateLandingsEPU.html). Work towards this ideal, comparing coverage of VTR data by species and different methods for scaling as part of data documentation. Consult with ADIOS team and assessment experts to see if results look reasonable.
